iSEE: Interactive SummarizedExperiment Explorer

### 2018-04-12 manuscript/main.tex
last typo (I hope)

\title[iSEE]{iSEE: Interactive SummarizedExperiment Explorer}
\author[Rue-Albrecht \textit{et~al}.]{Kevin Rue-Albrecht\,$^{\text{\sfb 1,}\dagger}$,
    Federico Marini\,$^{\text{\sfb 2,3,}\dagger}$,
    Charlotte Soneson\,$^{\text{\sfb 4,}\dagger}$,
    and Aaron T. L. Lun\,$^{\text{\sfb 5,}\ast,\dagger}$}
\address{$^{\text{\sf 1}}$Kennedy Institute of Rheumatology, University of Oxford, Oxford OX3 7FY, United Kingdom, \\
$^{\text{\sf 2}}$Center for Thrombosis and Hemostasis (CTH), Mainz \\
$^{\text{\sf 3}}$Institute for Medical Biostatistics, Epidemiology and Informatics, Mainz \\
$^{\text{\sf 4}}$University of Zurich and SIB Swiss Institute of Bioinformatics \\
$^{\text{\sf 5}}$Cancer Research UK Cambridge Institute, University of Cambridge, Cambridge CB2 0RE, United Kingdom \\
$^{^\dagger}$These authors contributed equally.}

>>>>

\title[iSEE]{iSEE: Interactive SummarizedExperiment Explorer}
\author[Rue-Albrecht \textit{et~al}.]{Kevin Rue-Albrecht\,$^{\text{\sfb 1,}\dagger}$,
    Federico Marini\,$^{\text{\sfb 2,3,}\dagger}$,
    Charlotte Soneson\,$^{\text{\sfb 4,}\dagger}$,
    and Aaron T. L. Lun\,$^{\text{\sfb 5,}\ast,\dagger}$}
\address{$^{\text{\sf 1}}$Kennedy Institute of Rheumatology, University of Oxford, Oxford OX3 7FY, United Kingdom, \\
$^{\text{\sf 2}}$Center for Thrombosis and Hemostasis (CTH), Mainz, \\
$^{\text{\sf 3}}$Institute for Medical Biostatistics, Epidemiology and Informatics, Mainz, \\
$^{\text{\sf 4}}$University of Zurich and SIB Swiss Institute of Bioinformatics, and \\
$^{\text{\sf 5}}$Cancer Research UK Cambridge Institute, University of Cambridge, Cambridge CB2 0RE, United Kingdom\\
$^{^\dagger}$These authors contributed equally.}
